Envelope Estimation using Geometric Properties of a Discrete Real Signal

### 2021-05-06 Papers/01_Pulses_Envelope/PulsesEnvelope.tex
finished adding suggestions

To see that this condition holds for the proposed method, consider a discrete signal $ \mathbf{w} = (w_0, w_1, \cdots, w_{n-1}) $, where all the absolute values $ |P_j| $ of its local extrema are greater than one.

@@

% TODO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The third condition states what, for a periodic signal, the envelope should be a straight line with the intercept equal to the amplitude of this signal. Since all the local maxima have the same amplitude in the case of a periodic wave, our envelope will indeed be a straight line, with the same amplitude as the original wave. An example of such behaviour can be observed in Fig. \ref{fig:Comparison_sinusoid}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The fourth and last condition states that if a wave is multiplied by a constant, the envelope should also be multiplied by the same constant.

>>>>

To see that this condition holds for the proposed method, consider a discrete signal $ \mathbf{w} = (w_0, w_1, \cdots, w_{n-1}) $, where all the absolute values of its local extrema are greater than one.

@@

The third condition states that a physically plausible algorithm should, for a signal $ \mathbf{w} $ of constant amplitude $ a > 0, \ a \in \mathbb{R} $ and constant frequency, of the form $ a \cos(\omega i + \phi) $, result in a constant envelope $ \mathbf{e} $ of magnitude $ a $ and o a carrier wave $ \mathbf{c} $ of the form $ \cos(\omega i + \phi) $.

An example of such behaviour can be observed in Fig. \ref{fig:Comparison_sinusoid}, where the envelope of a simple sinusoid is shown. To see that this is always the case, note that all the extrema of a sinusoid are of the form $ a (\pm 1) $ and $ P_j = (i_j, \lvert a (\pm 1) \lvert) = (i_j, a) \ \forall P_j \in \text{P} $. As $ \text{E} \subset \text{P} $, we have that the envelope $ \mathbf{e} = (a, a, \cdots, a) $ and is, thus constant. Likewise, since $ \mathbf{w} = \mathbf{e} \odot \mathbf{c} $, we have $ c_i = a \cos(\omega i + \phi) / a = \cos(\omega i + \phi) \ \forall \ i, 0 \le i \le n - 1 $.

The fourth and last condition states that if a wave is multiplied by a constant, its envelope should also be multiplied by the same constant.
